Ensemble Super-Learning for State Estimation. \\Application to the reconstruction of urban pollution.

### 2023-09-01 paper/main.tex
Add plots in results.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/plot_barplot_mse_vs_models_by_None.pdf}
    \includegraphics[width=\linewidth]{figures/plot_barplot_mse_vs_station_by_models.pdf}
    \caption{Error plots.}
    \label{fig:errorplots}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/plot_pollution_map_in_graph_modelLR_Extra_stationOPERA.pdf}
    \includegraphics[width=\linewidth]{figures/plot_pollution_map_in_graph_modelNN_Extra_stationOPERA.pdf}
    \caption{Pollution maps.}
    \label{fig:pollutionmaps}
\end{figure}
